---
title: "Metaweb Assembly Simulations"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Setup

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)


# Check and install required packages
required_packages <- c(
  "lhs", "dplyr", "purrr", "igraph", "ggplot2", "tibble", "doFuture","devtools","abc", "tidyverse"
)
for (pkg in required_packages) {
  if (!requireNamespace(pkg, quietly = TRUE)) {
    install.packages(pkg, repos = "https://cloud.r-project.org")
  }
  require(pkg, character.only = TRUE)
}


# Install meweasmo from GitHub if not installed
if (!requireNamespace("meweasmo", quietly = TRUE)) {
  devtools::install_github("lsaravia/meweasmo")
}
library(meweasmo)

# Install multiweb from GitHub if not installed
if (!requireNamespace("multiweb", quietly = TRUE)) {
  devtools::install_github("lsaravia/multiweb")
}
library(multiweb)

source("R/network_fun.r")

# load network_info
network_info <- readRDS("Data/network_info.rds")
```

## Parameter Ranges and Simulation Settings and Run Simulations

```{r simulMetaWeb_NS, eval=FALSE, message=TRUE, warning=TRUE}

# Parameter ranges (adjust as needed)

par_ranges <- matrix(c(0.01, 0.3, 0.001, 0.5, 0.1, 0.9), nrow=3, byrow=TRUE)
nsims <- 10000
model_type <- 1 # or as needed for your function

if(FALSE) {
# Remove networks with "std" in the site name
  network_info <- network_info %>% filter(!grepl("std", site, ignore.case = TRUE))
} else {
# Only networks with "std" in the site name
  # network_info <- network_info %>% filter(grepl("std", site, ignore.case = TRUE))
  # network_info <- network_info[10:11,]
}  
# Function to run simulations for a single igraph object
run_simulation_for_network <- function(g, net_name) {
  A <- igraph::as_adjacency_matrix(g, sparse=FALSE)
  sim <- sim_metaWebAssembly_lhs(3, nsims, par_ranges, A, model_type) %>%
    mutate(model_type="Continuous", model="Prob", Metaweb=net_name)
  return(sim)
}

## Run Simulations for All Networks

# Assuming network_info has columns 'site' and 'igraph'
require(tictoc)
tic("Running simulations for all networks")
simMetaWebAssembly <- purrr::map2_dfr(
    network_info$igraph,
    network_info$site,
    run_simulation_for_network
  )
toc()

# Save results and add it to already simulated data
#
if (file.exists("Data/simulations_metaWebAssembly_all_networks.rds")) {
  simMetaWebAssembly <- bind_rows(simMetaWebAssembly, readRDS("Data/simulations_metaWebAssembly_all_networks.rds"))
  message("Add simulations to simMetaWebAssembly from RDS file.")
}

saveRDS(simMetaWebAssembly, "Data/simulations_metaWebAssembly_all_networks.rds")
```

## Fit Metaweb Assembly Model

```{r FitMetaWebAssembly, eval=FALSE, message=TRUE, warning=TRUE}
# if the file not exist load it
if (file.exists("Data/simulations_metaWebAssembly_all_networks.rds")) {
  simMetaWebAssembly <- readRDS("Data/simulations_metaWebAssembly_all_networks.rds")
  message("Loaded simMetaWebAssembly from RDS file.")
}

all_results_list <- purrr::pmap(
  list(
    emp_S = network_info$S,
    emp_C = network_info$C,
    web_name = network_info$site
  ),
  function(emp_S, emp_C, web_name) {
    #fit_metaWebAssembly_model(emp_S, emp_C, web_name, simMetaWebAssembly)
    CI_metaWebAssembly_model(emp_S, emp_C, web_name, simMetaWebAssembly)
  }
)

# and then row-binds them into a single data frame.
fittedMetaWeb <- purrr::map_dfr(all_results_list, "sel")

# Extract and combine the 'gof_rej_data' components into another data frame
gof_rej_df <- purrr::map_dfr(all_results_list, "gof")


## Save Fitted Results
if (file.exists("Data/fittedMetaWeb_all_networks.rds")) {
  f_MetaWeb <- readRDS("Data/fittedMetaWeb_all_networks.rds")
  fittedMetaWeb <- bind_rows(fittedMetaWeb, f_MetaWeb)
  message("Loaded simMetaWebAssembly from RDS file.")
}
if (file.exists("Data/gof_all_networks.rds")) {
  g_rej_all <- readRDS("Data/gof_all_networks.rds")
  gof_rej_df <- bind_rows(gof_rej_df, g_rej_all)
  message("Loaded gof_all_networks from RDS file.")
}

saveRDS(fittedMetaWeb, "Data/fittedMetaWeb_all_networks.rds")
saveRDS(gof_rej_df, "Data/gof_all_networks.rds")

fittedMetaWeb %>% filter(min_dist)
```
## Plot simulation ranges of parameters to check fit

```{r plotParRange, eval=FALSE, message=TRUE, warning=TRUE}

fittedMetaWeb <- readRDS("Data/fittedMetaWeb_all_networks.rds")

# Crear un data frame con los límites para facilitar el ploteo con facet_wrap
parameter_limits <- tibble::tibble(
  parameter = c("a", "m", "se"),
  min_val = par_ranges[, 1],
  max_val = par_ranges[, 2]
)

# --- Transformar fittedMetaWeb a formato largo para los parámetros m, a, se ---
fitted_long <- fittedMetaWeb %>%
  pivot_longer(
    cols = c(m, a, se), # Seleccionar las columnas de los parámetros a pivotar
    names_to = "parameter", # Nombre de la nueva columna que contendrá los nombres de los parámetros
    values_to = "value" # Nombre de la nueva columna que contendrá los valores de los parámetros
  )

# --- Graficar las distribuciones ---
plots <- list()
for (i in seq_along(network_info$site)) {
  net_name <- network_info$site[i]
  fl <- fitted_long %>% filter(Metaweb == net_name)
  p <- ggplot(fitted_long, aes(x = value)) +
    geom_density(fill = "steelblue", alpha = 0.7) + # O geom_histogram(bins = 30, fill = "steelblue", alpha = 0.7)
    facet_wrap(vars( parameter), scales = "free_x", ncol = 1) + # Un facet por parámetro, con escala x libre
    geom_vline(data = parameter_limits, aes(xintercept = min_val),
               linetype = "dashed", color = "red", size = 0.8) +
    geom_vline(data = parameter_limits, aes(xintercept = max_val),
               linetype = "dashed", color = "red", size = 0.8) +
    labs(
      title = net_name,
      x = "Valor del Parámetro",
      y = "Densidad"
    ) +
    theme_bw(base_size = 14) +
    theme(plot.title = element_text(hjust = 0.5))  # Centrar el título


  print(p)
}
# Opcional: Guardar el gráfico
# ggsave("parameter_distributions.png", plot = p, width = 8, height = 10, units = "in", dpi = 300)

```

## Plot a vs m for Each Network

```{r plotSvsC, eval=FALSE, message=TRUE, warning=TRUE}
library(ggplot2)

# Ensure simMetaWebAssembly has columns S, C, and Metaweb

# Loop over each network/site
plots <- list()
for (i in seq_along(network_info$site)) {
  net_name <- network_info$site[i]
  sim_data <- fittedMetaWeb %>% filter(Metaweb == net_name)
  
  p <- ggplot(sim_data, aes(x = a, y = m)) +
    geom_point(alpha = 0.3, color = "blue") +
    labs(
      title = paste( net_name),
      x = "a parameter",
      y = "m parameter"
    ) +
    theme_minimal()
  
    plots[[i]] <- p
}
plots

```

## Simulate for each network and calculate metrics

```{r simMetaWebMetrics_NS, eval=TRUE, message=TRUE, warning=TRUE}
# Load the fittedMetaWeb data
fittedMetaWeb <- readRDS("Data/fittedMetaWeb_all_networks.rds")

# Only networks with "std" in the site name
# network_info <- network_info %>% filter(!(site %in% c("WeddellSea","BeagleChannel")))
network_info <- network_info[10:11,]

if (file.exists("Data/simulations_metaWebAssembly_all_networks.rds")) {
  simMetaWebMetrics <- readRDS("Data/simulations_metaWeb_metrics.rds")
  message("Loaded simMetaWebAssembly from RDS file.")
} else {
  simMetaWebMetrics <- tibble::tibble()
}

require(tictoc)
tic()
simulated_metaweb_metrics <- lapply(seq_along(network_info$site), function(i) {
  message("Simulating for site: ", network_info$site[i])

  # Simulate metaweb metrics
  sim <- simulate_metaweb_metrics(as_adjacency_matrix(network_info$igraph[i][[1]],sparse=FALSE),
                                                      fittedMetaWeb, 
                          network_info$site[i], nsim=1000)

  return(sim)
})
simulated_metaweb_metrics <- bind_rows(simulated_metaweb_metrics)
toc()

simMetaWebMetrics <- bind_rows(simMetaWebMetrics, simulated_metaweb_metrics)

# Calculate Rank/S 

simMetaWebMetrics <- simMetaWebMetrics %>% mutate(relRank = Rank/S)

saveRDS(simMetaWebMetrics,"Data/simulations_metaWeb_metrics.rds")
```

# Plot Metaweb metrics vs empirical

```{r plotMetaWebMetrics, eval=FALSE, message=TRUE, warning=TRUE}
simMetaWebMetrics <- readRDS("Data/simulations_metaWeb_metrics.rds")
require(patchwork)
network_info <- filter(network_info, !(site %in% c("WeddellSea","BeagleChannel","NorthernScotia","SouthernScotia")))
network_info <- network_info %>% mutate(relRank=Rank/S)

plot_list <- plot_empirical_vs_simulated_metrics(network_info,simMetaWebMetrics, metrics=c("S", "C","relRank", "Entropy", "Modularity"))

combined_plot <- wrap_plots(plot_list, ncol = 2, guides = "collect", axes="collect_x") &
  theme(legend.position = "bottom")

ggsave("Figures/empirical_vs_simulated_metrics.png", 
          plot = combined_plot, 
          height = 6, 
          width = 10,
          bg = "white")

plot_list <- plot_empirical_vs_simulated_metrics(network_info,simMetaWebMetrics, metrics=c("LD", "TLmean","Vulnerability","Generality"))

combined_plot <- wrap_plots(plot_list, ncol = 2, guides = "collect", axes="collect_x") &
  theme(legend.position = "bottom")

ggsave("Figures/empirical_vs_simulated_metrics_LD_TL.png", 
          plot = combined_plot, 
          height = 6, 
          width = 10,
          bg = "white")
```

# Plot Metaweb metrics vs empirical


```{r plotMetaWebMetrics1, eval=FALSE, message=TRUE, warning=TRUE}
# plot_metric_densities_with_empirical(network_info,simulated_metaweb_metrics)
# plot_empirical_vs_simulated_ci(network_info,simMetaWebMetrics)

#
## Metrics vs Latitude and Area
#
 
plot_list <- plot_metric_vs_latitude_ci(network_info, simMetaWebMetrics,fit_model = TRUE, metrics = c( "C", "Entropy", "Modularity"))
qr_models <- plot_list$models

plots  <- plot_list$plots
# combined_plot <- wrap_plots(plot_list$plots, ncol = 2, guides = "collect", axes="collect_x") &
#   theme(legend.position = "bottom")
# 
# # Show plot
# ggsave("Figures/metric_Entropy_vs_latitude_ci.png", 
#           plot = combined_plot, 
#           height = 6, 
#           width = 10,
#           bg = "white")

plot_list <- plot_metric_vs_latitude_ci(network_info, simMetaWebMetrics,fit_model = FALSE, metrics = c( "C", "Entropy", "Modularity"),xvar = "log_area")

plots <- c(plots,plot_list$plots)

### I need to arrange the list to show two columns 
plots_grouped <- unlist(split(plots, names(plots)), recursive = FALSE)

combined_plot <- wrap_plots(plots_grouped, ncol = 2, guides = "collect", axes="collect") &
  theme(legend.position = "bottom")
ggsave("Figures/metric_Entropy_vs_lat_area_ci.png", 
          plot = combined_plot, 
          height = 6, 
          width = 10,
          bg = "white")


#
# Relative Rank Rank/S
# LD and TLmean
#
plot_list <- plot_metric_vs_latitude_ci(network_info, simMetaWebMetrics, metrics = c("LD", "TLmean","relRank") , fit_model = TRUE)
qr_models <- append(qr_models,plot_list$models)
plots <- c(plot_list$plots)

# combined_plot <- wrap_plots(plot_list$plots, ncol = 2, guides = "collect", axes="collect_x") &
#   theme(legend.position = "bottom")
# 
# ggsave("Figures/metric_LD_TL_vs_latitude_ci.png", 
#           plot = combined_plot, 
#           height = 6, 
#           width = 10,
#           bg = "white")
# 
plot_list <- plot_metric_vs_latitude_ci(network_info, simMetaWebMetrics, metrics = c("LD", "TLmean", "relRank"), 
                                        xvar = "log_area",fit_model=TRUE)
plots <- c(plots,plot_list$plots)
plots_grouped <- unlist(split(plots, names(plots)), recursive = FALSE)
names(plots_grouped)

# Add p1 p2
combined_plot <- wrap_plots(plots_grouped[[1]],
                            plots_grouped[[2]],
                            plots_grouped[[5]],
                            plots_grouped[[6]],
                            plots_grouped[[3]],
                            plots_grouped[[4]],
        ncol = 2, guides = "collect", axes="collect") &
        theme(legend.position = "bottom")

ggsave("Figures/metric_LD_TL_vs_lat_area_ci.png", 
          plot = combined_plot, 
          height = 6, 
          width = 10,
          bg = "white")

#qr_models <- c(qr_models, plot_list$models)
saveRDS(qr_models, "Data/qr_models.rds")
knitr::kable( summarize_quantreg_models(qr_models,variables = c("latitude","log(area_km2)","log_area")),digits=4)
```

|metric       |term          | estimate| p_value|
|:------------|:-------------|--------:|-------:|
|S            |latitude      |  -6.5533|  0.0000|
|S            |log(area_km2) |  17.1379|  0.0000|
|C            |latitude      |  -0.0006|  0.3833|
|C            |log(area_km2) |   0.0005|  0.8699|
|Rank         |latitude      |  -0.0568|  0.0454|
|Rank         |log(area_km2) |   6.0151|  0.0000|
|relRank      |latitude      |   0.0103|  0.0000|
|relRank      |log_area      |  -0.0066|  0.0000|
|Entropy      |latitude      |   0.0020|  0.0000|
|Entropy      |log(area_km2) |  -0.0044|  0.0000|
|Modularity   |latitude      |  -0.0047|  0.0000|
|Modularity   |log(area_km2) |  -0.0035|  0.0000|
|LD           |latitude      |  -0.5174|  0.0000|
|LD           |log(area_km2) |   1.3487|  0.0000|
|TLmean       |latitude      |  -0.0102|  0.0000|
|TLmean       |log(area_km2) |   0.1158|  0.0000|
|MEing_stable |latitude      |   0.0024|  0.0000|
|MEing_stable |log_area      |  -0.0080|  0.0000|
